Formalizing Stack Safety as a Security Property

### 2021-07-08 submission3/main.tex
Arthur's last name

Heap safety, like stack safety, may be framed as a security property using
the language of
noninterference~\citep{DBLP:conf/post/AmorimHP18}\iftrue\bcp{Should be
  spelled ``Azedevo et al.''  We should figure out how to make bibtex do
  that (or ask arthur how!).}\fi.  Their paper was a significant inspiration
for the present work, and we believe that the two safety conditions should
combine smoothly.

>>>>

Heap safety, like stack safety, may be framed as a security property using
the language of
noninterference~\citep{DBLP:conf/post/AmorimHP18}. Their paper was a significant inspiration
for the present work, and we believe that the two safety conditions should
combine smoothly.
